Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY

### 2016-01-01 Manuscript/Manuscript.Rnw
more joe changes

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\begin{document}
\maketitle
%
%%%%%%%%%%%% R %%%%%%%%%%%%
<<sweave,echo=FALSE>>=
  options(width=60)
  options(scipen=999)
  options(digits=3)

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
@
<<setup, include=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
library(stargazer)
library(tables)
library(xtable)
#
# File Structure
file_drive= "C:"
##file_drive="E:"
directory = paste0(file_drive,"/Dropbox/Lab/Research/Projects/Current/NLSY AFI")
#
# Functions
## source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")
## cor_1star
### Prints out clean correlation matrix. If you want to replace the upper triangle with the sample size, toggle include.n, whose default is FALSE.
cor_1star <- function(x,digit=3,sig=.05,include.n=FALSE){ 
  require(Hmisc) 
  x <- as.matrix(x) 
  R <- rcorr(x)$r 
  p <- rcorr(x)$P 
   ## truncate the matrix that holds the correlations to two decimal
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), digit))[,-1] 
  ## build a new matrix that includes the correlations with their appropriate stars 
  Rnew <- R
  if(!is.na(sig)){
  ## define notions for significance levels; spacing is important.
  mystars <- ifelse(p < sig, "* ", " ")

@@

@@

#### Age 11
capture.output(stargazer(ModelSummaries_Mplusg2_11,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2_11measurement.tex"))
capture.output(stargazer(g2loading_11,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2loading_11.tex"))
@
<<results_regression,echo=FALSE, comment=NA, include=FALSE,cache=FALSE>>=
# Stargazer Plot defaults
font.size="small"
no.space=TRUE
style="demography"
column.sep.width = "1pt"
header = FALSE
column.labels = c("Mixed", "Daughters", "Sons")
model.numbers=FALSE
float=FALSE
ci =TRUE
single.row = TRUE
# 9.5
capture.output(stargazer(model.meanmoms_9,model.meanmoms.g_9,model.meanmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex"))

@@

capture.output(latex(
  tabular(Heading("Year Born")*YRB + Heading("Standardized Ability Score")*zIntel_G2 + Heading("AFI")*AFI_G2 ~ (Heading("Has Sibling in NLSY?")*(Mean + Sd)*Heading()*(1 + RowFactor(SiblinginSample))), data = summarystats_g2),
  numeric.dollar=TRUE,na.blank=TRUE),
  file=paste0(directory,"/Common/content/tables/table_summary_stats_sibinsampleg2.tex"))
@

%%%%%%%%%%%% Introduction %%%%%%%%%%%%
%\section{Introduction}
\section{ }\vspace{-.8cm}
% Introduce the Major Problem
\input{../Common/content/writing/introduction.tex}
% Current Study
\subsection{Current Study, Summary}
\input{../Common/content/writing/current_study.tex}

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
\subsection{Research Design}
\input{../Common/content/writing/design.tex}
%
% Sample
\subsection{Sample}
\input{../Common/content/writing/subjects.tex}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/writing/tetrad.tex}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
% Age at First Intercourse
\subsection{Measures}
\input{../Common/content/writing/AFI.tex}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Smoothed Density Plots of AFI by Race and Sex}
\label{plot_afi_by_race_sex}
\begin{center}
<<plot_afi_by_race_sex,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.6, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=
  # Color Blind Palette 
  cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#000000")
  # Data Prep
  dataframe<-data.frame(Gen2AFIConcor_2,Gen2AFIConcor$Intel_G2)
  names(dataframe)<- c("CASEID","MCASEID","Race","SEX","AFI","Intel")

  ## Race by Sex factor
  dataframe$RacebySEX<-"0"
  ###
  ### Hispanic
  #### Male
  dataframe$RacebySEX[dataframe$Race=='Hispanic' & dataframe$SEX=='Male']<-"Hispanic Male"
  ####
  #### Female
  dataframe$RacebySEX[dataframe$Race=='Hispanic'&dataframe$SEX=='Female']<-"Hispanic Female"
  ###
  ### Black
  #### Male
  dataframe$RacebySEX[dataframe$Race=='Black'&dataframe$SEX=='Male']<-"Black Male"
  ####
  #### Female
  dataframe$RacebySEX[dataframe$Race=='Black'&dataframe$SEX=='Female']<-"Black Female"
  ###
  ### Non-Black, Non-Hispanic
  #### Male
  dataframe$RacebySEX[dataframe$Race=='Non-Black, Non-Hispanic'&dataframe$SEX=='Male']<-"White Male"
  ####
  #### Female
  dataframe$RacebySEX[dataframe$Race=='Non-Black, Non-Hispanic'&dataframe$SEX=='Female']<-"White Female"
  ###
  ### Unknown Race
  dataframe$RacebySEX[dataframe$RacebySEX=='0']<-"Unknown"
 dataframe$Race<-revalue(dataframe$Race, c("Non-Black, Non-Hispanic"="Non-Black,\nNon-Hispanic"))
  #summary(as.factor(dataframe$RacebySEX))

  ggplot(dataframe, aes(x=AFI, colour=Race, group=RacebySEX, linetype = SEX))+ geom_density(fill=NA,adjust=2)+ theme_bw() + theme(axis.text=element_text(size=10), axis.title=element_text(size=12), plot.title=element_text(size=12)) +  theme(legend.position="right",  legend.justification=c(1, 0.5),legend.text=element_text(size=8)) +   xlab("AFI") + ylab("Density") +scale_colour_manual(values= c("#56B4E9", "#009E73", "#CC79A7")) + coord_cartesian(ylim=c(0,0.30), xlim=c(12,25))
  @
\end{center}
\end{minipage}
%
% Intelligence
\input{../Common/content/writing/intelligence.tex}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
<<calculationalphadif,cache=FALSE,include=FALSE>>=
# Intelligence
sigmax = sqrt(1.1881)
sigmay = sigmax
rxx = .87
ryy = rxx
rxy=.67
r.diff.intelligence <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /(sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
#AFI
sigmax = sqrt(4.41)
sigmay = sigmax
rxx = .76
ryy = rxx
rxy=.099
r.diff.afi <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
Our design assumes that the difference scores of our measures are reliable. We've reported the test-retest reliability of Gen2 intelligence and Gen1 AFI in earlier sections. Here, we report the test-retest reliability of the pairwise differences of those measures. 
\subsubsection{AFI} Comparing sibling differences in AFI as reported in 1983 and 1984 (n = 783 pairs) we found a moderate correlation (r = .76). The sample of sibling pairs with complete information in 1985 was too small (n = 12 pairs) to compare to the other two years. Regardless, sibling differences in self-reported AFI appear satisfactory for research purposes. We note that the common concern with unreliability of difference scores is at least partially mitigated when the separate scores defining the differences are reliable themselves. Because we could not estimate test-retest reliabilities for Generation 2, we calculated the reliability using Lord's equation (\citeyear{Lord1963}). Generation 2 Mean AFI difference scores were also moderately reliable (r = \Sexpr{r.diff.afi}) and comparable to Generation 1 sibling differences.

@@

  \caption{Mean Joint Intelligence $\rightarrow$ Gen2 Mean AFI}\label{table_Mean_Joint_Intelligence_Mean_Child_AFI_10}

@@

  \caption{Gen1 Dif Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Mom_Intelligence_Dif_Child_AFI_10}

@@

  \caption{Gen2 Dif Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Child_Intelligence_Dif_Child_AFI_10}

@@

  \caption{Joint Dif Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Joint_Intelligence_Dif_Child_AFI_10}

@@

  \caption{Mean Joint Intelligence $\rightarrow$ Gen2 Mean AFI}\label{table_Mean_Joint_Intelligence_Mean_Child_AFI_11}

@@

  \caption{Gen1 Dif Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Mom_Intelligence_Dif_Child_AFI_11}

@@

  \caption{Gen2 Dif Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Child_Intelligence_Dif_Child_AFI_11}

@@

  \caption{Dif Joint Intelligence $\rightarrow$ Gen2 Dif AFI}\label{table_Dif_Joint_Intelligence_Dif_Child_AFI_11}

@@

\end{document}

>>>>

%%%%%%%%%%%% Title %%%%%%%%%%%%
\title{Is the Link Between Intelligence and Age at First Intercourse Causal or Correlational? \\ A Cross-Generational Sibling Comparison Design Using the NLSY}
\shorttitle{Intelligence and AFI}
%
% Authors and Affiliations
\author{S. Mason Garrison and Joseph Lee Rodgers}
\affiliation{Vanderbilt University}
%
% Author Note
\authornote{\input{../Common/content/title/authornote.tex}}
%
% Abstract
\abstract{Last compiled \today\ at \currenttime\\
\input{../Common/content/title/abstract_empreport.txt}}
%
% Key Words
\keywords{Age at first intercourse; Cross-sectional Data; Discordant Sibling Design; Intelligence; Quasi-Experimental; Siblings}
%
\begin{document}
\maketitle

%
%%%%%%%%%%%% R %%%%%%%%%%%%
<<sweave,echo=FALSE>>=
  options(width=60)
  options(scipen=999)
  options(digits=3)

  listing <- function(x, options){
    paste("\\begin{lstlisting}[style=Rsettings]\n",
      x, "\\end{lstlisting}\n", sep = "")}
  knit_hooks$set(source=listing, output=listing)
@
<<setup, include=FALSE>>=
# Libraries
## Install Most Current Version
library(devtools)#;dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("harrelfe/Hmisc");dev_mode(on=F)
## Attach Remaining
library(corrplot)
library(ggplot2);library(ggExtra)
library(Hmisc)
library(MplusAutomation)
library(NlsyLinks)
library(plyr);library(psych)
#library(stargazer)
library(tables)
library(xtable)
#
# File Structure
file_drive= "C:"
##file_drive="E:"
directory = paste0(file_drive,"/Dropbox/Lab/Research/Projects/Current/NLSY AFI")
#
# Functions
## source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")
#Modded Stargazer
source(paste0(directory,"/Common/content/functions/stargazer.R"))
source(paste0(directory,"/Common/content/functions/stargazer-internal.R"))
## cor_1star
### Prints out clean correlation matrix. If you want to replace the upper triangle with the sample size, toggle include.n, whose default is FALSE.
cor_1star <- function(x,digit=3,sig=.05,include.n=FALSE){ 
  require(Hmisc) 
  x <- as.matrix(x) 
  R <- rcorr(x)$r 
  p <- rcorr(x)$P 
 ## truncate the matrix that holds the correlations to two decimal
  R <- format(round(cbind(rep(-1.11, ncol(x)), R), digit))[,-1] 
## build a new matrix that includes the correlations with their appropriate stars 
  Rnew <- R
  if(!is.na(sig)){
## define notions for significance levels; spacing is important.
  mystars <- ifelse(p < sig, "* ", " ")

@@

Gen2AFIConcor_3 <- merge(Gen1AFIConcor,Gen2AFIConcor,by="MCASEID",all=T)
Gen2AFIConcor_3$Intel_G1_SE<-NULL
Gen2AFIConcor_3$Intel_G2_SE<-NULL
Gen2AFIConcor_3$ASEID<-NULL

@@

#### Age 11
capture.output(stargazer(ModelSummaries_Mplusg2_11,summary=FALSE,flip = TRUE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2_11measurement.tex"))
capture.output(stargazer(g2loading_11,summary=FALSE,flip = FALSE, dep.var.labels.include = FALSE),file=paste0(directory,"/Common/content/tables/table_g2loading_11.tex"))
@
<<results_regression,echo=FALSE, comment=NA, include=FALSE,cache=FALSE>>=
# Stargazer Plot defaults
font.size="small"
no.space=TRUE
style="demography"
column.sep.width = "1pt"
header = FALSE
column.labels = c("Mixed", "Daughters", "Sons")
model.numbers=FALSE
float=FALSE
ci =TRUE
single.row = TRUE
notes.append = TRUE
# 9.5
capture.output(stargazer(model.meanmoms_9,model.meanmoms.g_9,model.meanmoms.b_9,
                         font.size=font.size,
                         no.space=no.space,
                         column.sep.width = column.sep.width,
                         header = header,
                         covariate.labels=c("Gen1 Mean Intel"), 
                         dep.var.labels=c("Gen2 Mean AFI"),
                         column.labels = column.labels,
                         model.numbers=model.numbers,
                         float=float,
                         ci =ci,
                         single.row = single.row),
               file=paste0(directory,"/Common/content/tables/table_Mean_Mom_Intelligence_Mean_Child_AFI_9.tex"))

@@

capture.output(latex(
  tabular(Heading("Year Born")*YRB + Heading("Standardized Ability Score")*zIntel_G2 + Heading("AFI")*AFI_G2 ~ (Heading("Has Sibling in NLSY?")*(Mean + Sd)*Heading()*(1 + RowFactor(SiblinginSample))), data = summarystats_g2),
  numeric.dollar=TRUE,na.blank=TRUE),
  file=paste0(directory,"/Common/content/tables/table_summary_stats_sibinsampleg2.tex"))
@
<<figurestyle,include=FALSE>>=
# Color Blind Palette 
  cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#000000")

# Ribbon Color
ribbonfill='seagreen3'
ribbonalpha=.35
# Function adapted from http://stackoverflow.com/questions/4094094/modifying-fonts-in-ggplot2
theme_min = function (size=10, font=NA, face='plain',
                      axisColor='#999999',
                      textColor='black'){
  element_text = function(...)

  ggplot2::element_text(#family=font, face=face,
    colour=textColor, size=size, ...)

  theme(
    axis.text.x = element_text(),
    axis.text.y = element_text(),
    axis.line = element_blank(),
    axis.ticks = element_line(colour=axisColor, size=0.25),

    legend.key = element_rect(fill = 'white', size = 0.5),
    legend.text = element_text(hjust=0),
    legend.title = element_text(hjust=0),

    panel.background = element_rect(fill = "white",colour = NA),
	  panel.border = element_rect(fill = NA,colour = "grey50"),
    panel.grid.major = element_line(colour = "grey90", size = 0.2),
	  panel.grid.minor = element_line(colour = "grey98", size = 0.5),
	  plot.title = element_text(hjust=0),
	  strip.background = element_rect(fill = "grey80", colour = "grey50", size = 0.2),
    strip.text.x = element_text(hjust=0),
    strip.text.y = element_text(angle=-90)
  )}
@
%%%%%%%%%%%% Introduction %%%%%%%%%%%%
%\section{Introduction}
\section{ }\vspace{-.8cm}
% Introduce the Major Problem
\input{../Common/content/writing/introduction.tex}
% Current Study
\subsection{Current Study, Summary}
\input{../Common/content/writing/current_study.tex}

%%%%%%%%%%%% Method %%%%%%%%%%%%
\section{Method}
\subsection{Research Design}
\input{../Common/content/writing/design.tex}
%
% Sample
\subsection{Sample}
\input{../Common/content/writing/subjects.tex}
%
% Tetrads
\subsection{Tetrads}
\input{../Common/content/writing/tetrad.tex}
%
%%%%%%%%%%%% Measurement %%%%%%%%%%%%
% Age at First Intercourse
\subsection{Measures}
\input{../Common/content/writing/AFI.tex}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Smoothed Density Plots of AFI by Race and Sex}
\label{plot_afi_by_race_sex}
\begin{center}
<<plot_afi_by_race_sex,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".65\\paperwidth",warning=FALSE>>=
# Data Prep
dataframe<-data.frame(Gen2AFIConcor_2,Gen2AFIConcor$Intel_G2)
names(dataframe)<- c("CASEID","MCASEID","Race","SEX","AFI","Intel")

## Race by Sex factor
  dataframe$RacebySEX<-"0"
###
### Hispanic
#### Male
  dataframe$RacebySEX[dataframe$Race=='Hispanic' & dataframe$SEX=='Male']<-"Hispanic \nMale"
####
#### Female
  dataframe$RacebySEX[dataframe$Race=='Hispanic'&dataframe$SEX=='Female']<-"Hispanic \nFemale"
###
### Black
#### Male
  dataframe$RacebySEX[dataframe$Race=='Black'&dataframe$SEX=='Male']<-"Black \nMale"
####
#### Female
  dataframe$RacebySEX[dataframe$Race=='Black'&dataframe$SEX=='Female']<-"Black \nFemale"
###
### Non-Black, Non-Hispanic
#### Male
  dataframe$RacebySEX[dataframe$Race=='Non-Black, Non-Hispanic'&dataframe$SEX=='Male']<-"Non-Black, Non-Hispanic Male"
####
#### Female
  dataframe$RacebySEX[dataframe$Race=='Non-Black, Non-Hispanic'&dataframe$SEX=='Female']<-"Non-Black, Non-Hispanic Female"
###
### Unknown Race
  dataframe$RacebySEX[dataframe$RacebySEX=='0']<-"Unknown"
 dataframe$Race<-revalue(dataframe$Race, c("Non-Black, Non-Hispanic"="Non-Black,\nNon-Hispanic"))
 dataframe$RacebySEX<-revalue(dataframe$RacebySEX, c("Non-Black, Non-Hispanic Female"="Non-Black,\nNon-Hispanic \nFemale"))
  dataframe$RacebySEX<-revalue(dataframe$RacebySEX, c("Non-Black, Non-Hispanic Male"="Non-Black,\nNon-Hispanic \nMale"))
#summary(as.factor(dataframe$RacebySEX))

ggplot(dataframe, aes(x=AFI, colour=RacebySEX, group=RacebySEX, linetype = RacebySEX))+ geom_density(fill=NA,adjust=2)+ theme_min(size=10)+  
    theme(legend.position="bottom",
          legend.justification=c(1, 0.5),
          legend.text=element_text(size=6),
          legend.key = element_rect(fill = 'white', size = 0.5),
          legend.title = element_blank()) +   
    xlab("AFI") + 
    ylab("Density") +
    scale_colour_manual(values= c("#56B4E9","#56B4E9", "#009E73", "#009E73", "#CC79A7", "#CC79A7")) +
    coord_cartesian(ylim=c(0,0.25), xlim=c(12,25)) +
    scale_linetype_manual(values=c(1,2,1,2,1,2))
  @
\end{center}
\end{minipage}
%
% Intelligence
\input{../Common/content/writing/intelligence.tex}
%
% Difference Score Reliability
\subsection{Reliability of Difference Scores}
<<calculationalphadif,cache=FALSE,include=FALSE>>=
# Intelligence
sigmax = sqrt(1.1881)
sigmay = sigmax
rxx = .87
ryy = rxx
rxy=.67
r.diff.intelligence <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) /(sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
#AFI
sigmax = sqrt(4.41)
sigmay = sigmax
rxx = .76
ryy = rxx
rxy=.099
r.diff.afi <- (sigmax*sigmax*rxx +sigmay*sigmay*ryy -2*rxy*sigmax*sigmay) / (sigmax*sigmax + sigmay*sigmay -2*rxy*sigmax*sigmay)
@
Our design assumes that the difference scores of our measures are reliable. We've reported the test-retest reliability of Gen2 intelligence and Gen1 AFI in earlier sections. Here, we report the test-retest reliability of the pairwise differences of those measures. 
\subsubsection{AFI} Comparing sibling differences in AFI as reported in 1983 and 1984 (n = 783 pairs) we found a moderate correlation (r = .76). The sample of sibling pairs with complete information in 1985 was too small (n = 12 pairs) to compare to the other two years. Regardless, sibling differences in self-reported AFI appear satisfactory for research purposes. We note that the common concern with unreliability of difference scores is at least partially mitigated when the separate scores defining the differences are reliable themselves. Because we could not estimate test-retest reliabilities for Generation 2, we calculated the reliability using Lord's equation (\citeyear{Lord1963}). Generation 2 Mean AFI difference scores were also moderately reliable (r = \Sexpr{r.diff.afi}) and comparable to Generation 1 sibling differences.

@@

  \caption{Joint Mean Intelligence $\rightarrow$ Gen2 Mean AFI}\label{table_Mean_Joint_Intelligence_Mean_Child_AFI_10}

@@

  \caption{Gen1 Intelligence Differences $\rightarrow$ Gen2 AFI Differences}\label{table_Dif_Mom_Intelligence_Dif_Child_AFI_10}

@@

  \caption{Gen2 Intelligence Differences $\rightarrow$ Gen2 AFI Differences}\label{table_Dif_Child_Intelligence_Dif_Child_AFI_10}

@@

  \caption{Joint Intelligence Differences $\rightarrow$ Gen2 AFI Differences}\label{table_Dif_Joint_Intelligence_Dif_Child_AFI_10}

@@

  \caption{Joint Mean Intelligence $\rightarrow$ Gen2 Mean AFI}\label{table_Mean_Joint_Intelligence_Mean_Child_AFI_11}

@@

  \caption{Gen1 Intelligence Differences $\rightarrow$ Gen2 AFI Differences}\label{table_Dif_Mom_Intelligence_Dif_Child_AFI_11}

@@

  \caption{Gen2 Intelligence Differences $\rightarrow$ Gen2 AFI Differences}\label{table_Dif_Child_Intelligence_Dif_Child_AFI_11}

@@

  \caption{Joint Intelligence Differences $\rightarrow$ Gen2 AFI Differences}\label{table_Dif_Joint_Intelligence_Dif_Child_AFI_11}

@@

\begin{landscape}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Generation 1: Age at First Intercourse vs. Intelligence}
\label{plot_gen1_afi}
\begin{center}
<<plot_gen1_afi,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=
library(ggplot2)
library(gtable)
library(grid)
library(gridExtra)
library(NlsyLinks)
# Gen 1 Plot
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsOutcomes <- Gen1AFIConcor
dsOutcomes$Sex<-testretest$SEX
dsOutcomes$SubjectTag <-dsOutcomes$MCASEID*100
dsD <- CreatePairLinksDoubleEntered(
outcomeDataset = dsOutcomes,
linksPairDataset = dsLinking,
outcomeNames = c("Intel_G1","AFI_G1","Sex"))
dsD$DIF_G<-#abs
  (dsD$Intel_G1_S1-dsD$Intel_G1_S2)
dsD$DIF_A<-#abs
  (dsD$AFI_G1_S1-dsD$AFI_G1_S2)
#m<-data.frame(Gen2AFIConcor$Intel_G2,Gen2AFIConcor$AFI_G2)

shading<-c("navy","dodgerblue4","dodgerblue3","dodgerblue2","lightsteelblue1","dodgerblue2","dodgerblue3","dodgerblue4","navy")
shading<-c("firebrick4",#"firebrick3","firebrick2",
           "firebrick1",#"mediumvioletred",
             "dodgerblue1",#"dodgerblue2","dodgerblue3",
           "dodgerblue4")
max_val <- max(abs(dsD$DIF_G),na.rm=TRUE)
values <- seq(-max_val, max_val, length = length(shading))
##############
ggplot(dsD, aes(y=AFI_G1_S1, x=Intel_G1_S1,colour=(DIF_G))) + 
  geom_point(size =1,alpha = 1,na.rm=TRUE,position = position_jitter(w = 0.1, h = 0.5)) +
  scale_colour_gradientn(name="Sibling \nDifferences \nin AFQT",colours=shading,values=values,rescaler = function(x, ...) x, oob = identity)+
  theme_min(size=10) +
     theme(plot.title=element_text(size=16,face="bold"))+ 
  ylab("Age at First Intercourse") +
  xlab("AFQT (Z Score)") #+
#ggtitle("Generation 1:\n Age at First Intercourse vs. Intelligence")

@
\end{center}
\end{minipage}
\noindent\begin{minipage}{\linewidth}
\captionof{figure}{Generation 2: Age at First Intercourse vs. Intelligence}
\label{plot_gen2_afi}
\begin{center}
<<plot_gen2_afi,fig=TRUE,echo=FALSE,cache=FALSE,echo=FALSE, fig.height=5*.8, fig.width=5,out.width=".8\\paperwidth",warning=FALSE>>=

# Gen 2 Plot
dsLinking <- subset(Links79Pair, RelationshipPath=="Gen1Housemates")
dsOutcomes <- Gen2AFIConcor_3

dsOutcomes$SubjectTag <-dsOutcomes$MCASEID*100
dsOutcomes<-dsOutcomes[!is.na(dsOutcomes$SubjectTag),]
ds2D <-dsOutcomes#
max_val <- max(abs(ds2D$Intel_G1),na.rm=TRUE)
values <- seq(-max_val, max_val, length = length(shading))
##############
ggplot(ds2D, aes(y=AFI_G2, x=Intel_G2,colour=(Intel_G1))) + 
  geom_point(size =1,alpha = 1,na.rm=TRUE,position = position_jitter(w = 0.01, h = 0.5)) +
  scale_color_gradientn(values=values,rescaler = function(x, ...) x, oob = identity,name="Maternal\n AFQT",colours=shading)+
  theme_min(size=10) +
     theme(plot.title=element_text(size=16,face="bold"))+ 
  ylab("Age at First Intercourse") +
  xlab("General Cognitive Ability") #+
#ggtitle("Generation 1:\n Age at First Intercourse vs. Intelligence")

@
\end{center}
\end{minipage}\end{landscape}
\end{document}
